Visualization and analysis of probability distributions of large temporal data

### 2021-11-05 Rmd/05-conclusion.Rmd
conclusion first chapter done

In this thesis, I present a systematic approach for visualizing and analyzing large temporal data distributions. The building blocks of this framework are presented in this thesis. Chapter \@ref(ch:gravitas) includes tools for computing all cyclic granularities as well as a recommendation system for selecting pairs of granularities that may be effectively investigated together. These temporal granularities may be used to generate data visualizations to search for patterns, associations, and anomalies. However, when there are many granularities that can be constructed for a time period, there will also be too many possible displays to decide which might be the more interesting to display. Chapter \@ref(ch:hakear) presents a framework for selecting displays that are interesting, with the greatest differences between the displayed distributions, and ranking them in order of priority for capturing the most variation. Both of these are used for studying patterns in individual time series or comparing a few time series together. In Chapter \@ref(ch:gracsr), it is extended to allow for the exploration of distributions for many time series at the same time by clustering them based on probability distributions across informative cyclic granularities. Through the use of probability distribution, this technique is more comprehensive in recognizing clusters with recurring patterns over many important granularities and more resilient to noisy, patchy, and uneven length time series.

>>>>

In this thesis, I present a systematic approach for visualizing and analyzing distributions of large temporal data by leveraging time characteristics. The building blocks of this framework are presented in each chapter. Chapter \@ref(ch:gravitas) contains tools for computing all cyclic granularities, as well as a recommendation system for selecting pairs of granularities that can be effectively analyzed together. These temporal granularities can be used to generate data visualizations to look for patterns, associations, and anomalies. But it is difficult to decide which of the various granularities to display when there are many options. Chapter \@ref(ch:hakear) presents a methodology for selecting displays that are interesting, such that differences between displayed distributions are greatest. The methodology also ranks the displays in order of priority for capturing the most variation. Both \@ref(ch:gravitas) and \@ref(ch:hakear) are used for studying patterns in individual time series or comparing a few time series together. This is extended in Chapter @ref(ch:gracsr) to allow for the exploration of distributions for multiple time series at the same time using unsupervised clustering. The clustering methodology produces small groups of time series with similar distributions over multiple granularities. This technique is more robust to noisy, patchy, and uneven length time series because it makes use of probability distributions.

<!-- is more comprehensive in recognizing clusters with recurring patterns over many important granularities and -->
